### 2022-09-01 main/chapter_searches.tex
add figures for frequentist section --- likelihoods and tail areas

This expression as an integral --- an average over the prior, means that
the evidence $Z$ depends on what fraction of samples hits large values of
the likelihood function, and not only on how large that likelihood gets.
In contrast, one could consider a maximum likelihood approach that would
constrain a numerical optimization to regions of nonzero prior in each model.
Such optimizations can give a useful upper bound on $Z$, but this example
highlights a flaw when both models support the $\met > 100\,\eV[G]$ bin.
Then, both support the same maximum likelihood of
$L(\varepsilon + 100\,\eV[G]) = 1$, despite different evidence values.

@@

\TODO{
Fisher:
criteria for estimators,
(consistency, efficiency, sufficiency)
~\cite{fisher1922estimators}
testing, p-value,
likelihood, also ratios of p-values (here named probable errors)
(introduced the term likelihood? cite?)
~\cite{fisher1921probable}
tail area = significance
~\cite{fisher1925smrw}
}

@@

>>>>

This expression as an integral --- an average over the prior, means that
the evidence $Z$ depends on what fraction of samples hits large values of
the likelihood function, and not only on how large that likelihood gets.
In contrast, one could consider a maximum likelihood approach that would
constrain a numerical optimization to regions of non-zero prior in each model.
Such optimizations can give useful upper bounds on the evidence, but this
example highlights a flaw when both models support the $\met > 100\,\eV[G]$
bin.
Then, both support the same maximum likelihood of
$L(\varepsilon + 100\,\eV[G]) = 1$, despite different evidence values.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.95\textwidth]{figures/seacrhes_fisher_likelihood_binomial.png}
\caption[
Ratio thresholds of a Binomial likelihood function, reproduced from Fisher
]{%
Ratio thresholds of a Binomial likelihood function, reproduced from
Fisher~\cite{fisher1956statistical}.
Levels are drawn at $1/2$, $1/5$, and $1/15$ of its maximum, as a practical way
to communicate its profile.
}
\label{fig:searches_fisher_likelihood}
\end{figure}

\TODO{
Fisher:
criteria for estimators,
(consistency, efficiency, sufficiency)
~\cite{fisher1922estimators}
testing, p-value,
likelihood, also ratios of p-values (here named probable errors)
(introduced the term likelihood? cite?)
~\cite{fisher1921probable}
tail area = significance
~\cite{fisher1925smrw}
}
Figure~\ref{fig:searches_fisher_likelihood}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.95\textwidth]{figures/searches_np_curves_crop.png}
\caption[
Tail areas of prior data distributions from two alternative hypotheses,
reproduced from Neyman and Pearson
]{%
Tail areas of prior data distributions from two alternative hypotheses,
reproduced from Neyman and Pearson~\cite{neymanpearson19233lemma}.
}
\label{fig:searches_np_tails}
\end{figure}

Figure~\ref{fig:searches_np_tails}

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/searches_atlas_higgs_4l_2207_00320.pdf}
\caption[
Signal and background distributions reproduced from the recent \atlas\
measurement of Higgs boson decays to $4\ell$
]{%
Signal and background distributions reproduced from the recent \atlas\
measurement of Higgs boson decays to $4\ell$~\cite{ATLAS:2022net}.
}
\label{fig:atlas_higgs_4l}
\end{figure}

Figure~\ref{fig:atlas_higgs_4l}
